# Tourism Dataset Regression Model Building

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE, warning=FALSE)
```

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(broom)
library(MASS)
library(caret)
library(car)
library(gridExtra)
```

## Read and Transform Data

```{r, message=FALSE, warning=FALSE}
tourism_df <- read.csv("../data/processed/full_tourism_dataset.csv")

tourism_df <- tourism_df %>% 
  filter(year < 2020) %>% 
  filter(total_inbound_tourism_expenditure >= 0 | total_arrivals >= 0) %>% 
  mutate(world_region = as.factor(world_region),
         hdi_code = as.factor(hdi_code))

tourism_df <- tourism_df %>% 
  mutate(tourism_grew = as.factor(ifelse(inbound_tourism_expenditure_growth >= 0.05, "Y", "N"))) %>% 
  mutate(log_gdp = log(gdp),
         log_gdp_per_capita = log(gdp_per_capita),
         log_total_inbound_tourism_expenditure = log(total_inbound_tourism_expenditure))
```

## Multiple Linear Regression Model 1 - Macroeconomic Indicators to Predict Tourism Income

### Initial Models

```{r}
income_model_df <- tourism_df %>% 
  dplyr::select(country,
                year,
                total_inbound_tourism_expenditure,
                log_total_inbound_tourism_expenditure,
                gdp_per_capita,
                log_gdp_per_capita,
                gdp,
                log_gdp,
                exchange_rate,
                cpi,
                hdi,
                unemployment_rate,
                hdi_code,
                world_region) %>% 
  na.omit()

####################################
## initial model - no interaction ##
####################################
income_model1 <- lm(log_total_inbound_tourism_expenditure~
                     log_gdp_per_capita+
                     log_gdp+
                     exchange_rate+
                     cpi+
                     hdi+
                     unemployment_rate+
                     hdi_code+
                     world_region, data = income_model_df)
summary(income_model1)

#################################
## initial model - interaction ##
#################################
income_model2 <- lm(log_total_inbound_tourism_expenditure~
                     log_gdp_per_capita+
                     log_gdp+
                     exchange_rate+
                     cpi+
                     unemployment_rate+
                     cpi*hdi_code+
                     cpi*world_region+
                     hdi_code+
                     world_region, data = income_model_df)
summary(income_model2)
```

### Varible Selection

#### Step-Wise AIC
```{r}
###################
## step-wise AIC ##
###################
aic <- MASS::stepAIC(income_model2, direction = "both", trace = F)
summary(aic) 
# removed exchange rate and gdp_per_capita
```

#### Ridge Regression

```{r}
###################
## design matrix ##
###################
X <- model.matrix(log_total_inbound_tourism_expenditure~
                    0+
                    log_gdp_per_capita+
                    log_gdp+
                    exchange_rate+
                    cpi+
                    unemployment_rate+
                    cpi*hdi_code+
                    cpi*world_region+
                    hdi_code+
                    world_region, data = income_model_df)

y <- income_model_df$log_total_inbound_tourism_expenditure

######################
## ridge regression ##
######################
ridge_income_model <- glmnet(x = X, y = y, alpha = 0)
ridge_k_cv_glmnet <- cv.glmnet(x = X, y = y, alpha = 0, nfolds = 10)
plot(ridge_income_model, label = T, xvar = "lambda") + abline(v = log(ridge_k_cv_glmnet$lambda.1se))
predict(ridge_income_model, type = "coefficient", s = ridge_k_cv_glmnet$lambda.1se, newx = X)

# based on ridge regression, we would remove exchange rate, and interaction terms
```

#### Lasso Regression

```{r}
######################
## lasso regression ##
######################
lasso_income_model <- glmnet(x = X, y = y, alpha = 1)
lasso_k_cv_glmnet <- cv.glmnet(x = X, y = y, alpha = 0, nfolds = 10)
plot(lasso_income_model, label = T, xvar = "lambda") + abline(v = log(lasso_k_cv_glmnet$lambda.1se))
predict(lasso_income_model, type = "coefficient", s = lasso_k_cv_glmnet$lambda.1se, newx = X)

# lasso would only keep gdp, gdp gdp per capita, cpi, and hdi_code
```

### Model Evals

```{r}
# use trainControl() function for applying cross validation methods
control <- trainControl(method = "repeatedcv", number = 10, repeats = 10)

aic_model <- train(log_total_inbound_tourism_expenditure~
                     log_gdp+
                     cpi+
                     unemployment_rate+
                     cpi*hdi_code+
                     cpi*world_region+
                     hdi_code+
                     world_region,
                   method = "lm", trControl = control, data = income_model_df)

# model assessment
aic_model$results$RMSE
aic_model$results$Rsquared
aic_model$results$MAE

# train model, with control cv function
ridge_model <- train(log_total_inbound_tourism_expenditure~
                       log_gdp_per_capita+
                       log_gdp+
                       cpi+
                       hdi_code+
                       world_region,
                      method = "lm", trControl = control, data = income_model_df)

# model assessment
ridge_model$results$RMSE
ridge_model$results$Rsquared
ridge_model$results$MAE

# train model, with control cv function
lasso_model <- train(log_total_inbound_tourism_expenditure~
                       log_gdp_per_capita+ 
                       log_gdp+
                       cpi+
                       hdi_code,
                      method = "lm", trControl = control, data = income_model_df)

# model assessment
lasso_model$results$RMSE
lasso_model$results$Rsquared
lasso_model$results$MAE
```

```{r}
# get VIF values
car::vif(lasso_model$finalModel)
```

### Model Assumptions

```{r, fig.height=7.5, fig.width = 15}
#######################
## model assumptions ##
#######################

p1 <- ggplot(income_model_df, aes(x = log_gdp_per_capita, y = log_total_inbound_tourism_expenditure)) +
  geom_point(color = "navy", alpha = 0.8) + 
  geom_smooth(method = "lm", se = F, color = "red") +
  theme_minimal() +
  labs(x = "ln(GDP Per Capita)", y = "ln(Tourism Income)") +
  theme(axis.title = element_text(face = "bold"))

p2 <- ggplot(income_model_df, aes(x = log_gdp, y = log_total_inbound_tourism_expenditure)) +
  geom_point(color = "navy", alpha = 0.8) + 
  geom_smooth(method = "lm", se = F, color = "red") +
  theme_minimal() +
  labs(x = "ln(GDP)", y = "ln(Tourism Income)") +
  theme(axis.title = element_text(face = "bold"))

p3 <- ggplot(income_model_df, aes(x = cpi, y = log_total_inbound_tourism_expenditure)) +
  geom_point(color = "navy", alpha = 0.8) + 
  geom_smooth(method = "lm", se = F, color = "red") +
  scale_x_continuous(limits = c(0,150)) +
  theme_minimal() +
  labs(x = "CPI", y = "ln(Tourism Income)") +
  theme(axis.title = element_text(face = "bold"))

grid.arrange(p1,p2,p3, nrow = 2)
```


```{r, fig.width=7, fig.height = 6}
income_final_model <- lm(log_total_inbound_tourism_expenditure~
                     log_gdp_per_capita+ 
                     log_gdp+
                     cpi+
                     hdi_code,
                   data = income_model_df)

# predictions, residuals on fitted model
income_model_preds <- mutate(income_model_df, predictions = fitted(income_model), resid = residuals(income_model))

# residual plot
ggplot(income_model_preds, aes(x = predictions, y = resid)) +
  geom_hline(yintercept = 0, color = "red", size = 1.1) +
  geom_point(size = 2.5, alpha = 0.5) +
  labs(x = "Predicted ln(Tourism Income)", y = "Residual") +
  #scale_x_continuous(limits = c(0,50000))
  theme_minimal() +
  theme(strip.background = element_rect(fill="gray90"),
        strip.text = element_text(size = 18, face = "bold")) +
  theme(axis.title = element_text(face = "bold"))

## qq plot
ggplot(income_model_preds, aes(sample = resid)) +
  stat_qq_line(size = 1, color = "red") +
  stat_qq(size = 3, alpha = 0.6) +
  labs(x = "Theoretical", y = "Sample") +
  theme_minimal() +
  theme(strip.background = element_rect(fill="gray90"),
        strip.text = element_text(size = 18, face = "bold")) +
  theme(axis.title = element_text(face = "bold"))
```

### Model Training

```{r}
####################
## model training ##
####################
set.seed(6021)

# use trainControl() function for applying cross validation methods
control <- trainControl(method = "repeatedcv", number = 10, repeats = 100)

# train model, with control cv function
income_trained_model <- train(log_total_inbound_tourism_expenditure~
                       log_gdp_per_capita+ 
                       log_gdp+
                       cpi+
                       hdi_code,
                      method = "lm", trControl = control, data = income_model_df)

# model summary
summary(income_trained_model)
```

### Predictions and Model Assessment

```{r}
set.seed(6021)

# model assessment
income_trained_model$results$RMSE
income_trained_model$results$Rsquared
income_trained_model$results$MAE

# make predictions
predictions <- exp(predict(income_trained_model, income_model_df))

# get predictions interval into data frame
pred_intervals <- data.frame(exp(predict(income_trained_model, newdata = income_model_df, interval = "prediction", level = 0.95)))
colnames(pred_intervals) <- "predicted"

# display outcomes
pred_df <- income_model_df %>% 
  dplyr::select(country, year, total_inbound_tourism_expenditure) %>% 
  mutate(pred = pred_intervals$predicted)

pred_df_view <- pred_df[sample.int(nrow(pred_df), 10),] 

pred_df_view <- pred_df_view %>% 
  rename(observed = total_inbound_tourism_expenditure)

# summarize predictions results
results <- income_model_df %>% 
  mutate(preds = predictions,
         observed = total_inbound_tourism_expenditure) %>% 
  mutate(diff = observed - preds,
         abs_diff = abs(observed - preds)) %>% 
  mutate(pct_diff = 100 * (abs_diff / abs(observed))) 

# get RMSE, MAE and MAPE on predicted values, non-log
print(paste0("RMSE: ",round(sqrt(mean(results$diff^2)), 3)))
print(paste0("MAE: ",round(mean(results$abs_diff),3)))
print(paste0("MAPE: ",round(mean(results$pct_diff),3),"%"))
```


## Multiple Linear Regression Model 2 - Infrastructure to Preidct Tourism Income

### Initial Model
```{r}
infrastructure_model_df <- tourism_df %>% 
  dplyr::select(bed_places, occupancy_rate_per_bed_place,
                establishments,rooms,total_tourism_employees,world_region,country,occupancy_rate_per_room,
                year,log_total_inbound_tourism_expenditure,total_inbound_tourism_expenditure,
                hdi_code) %>%
  na.omit()

infrastructure_model <-lm(log_total_inbound_tourism_expenditure~
                            bed_places+
                            occupancy_rate_per_room+occupancy_rate_per_bed_place+
                            establishments+rooms+
                            total_tourism_employees+
                            hdi_code+
                            world_region, 
                          data = infrastructure_model_df)

summary(infrastructure_model)
```

### Variable Selection

```{r}
# aic for variable selection
aic_model <- MASS::stepAIC(infrastructure_model, direction = "both", trace = F)
summary(aic_model) 
```

```{r}
vif_values <- data.frame(car::vif(aic_model))

ggplot(vif_values, aes(x = rownames(vif_values), y = GVIF)) + 
  geom_bar(stat = "identity", fill = "navy") + 
  geom_text(aes(label = format(round(GVIF,2), nsmall = 2)),
            position = position_dodge(width= 1), 
            hjust = -0.1,
            size = 4.3
            ) +
  geom_hline(yintercept = 5, linetype = "dashed", color = "gold") + 
  geom_hline(yintercept = 10, linetype = "dashed", color = "red") +
  scale_y_continuous(limits = c(0,40), breaks = seq(0,40,by=5)) +
  coord_flip() + 
  labs(y= "VIF", x= "Feature") +
  theme_minimal() +
  theme(axis.text=element_text(size=8)) +
  theme(axis.title = element_text(face = "bold"),
        axis.text.y = element_text(face = "italic"))
```

```{r}
# remove high VIF - rooms
infrastructure_model2<-lm(log_total_inbound_tourism_expenditure~
                            occupancy_rate_per_room+
                            occupancy_rate_per_bed_place+
                            establishments+
                            total_tourism_employees+
                            hdi_code+
                            world_region, 
                          data = tourism_df)

summary(infrastructure_model2)

vif(infrastructure_model2)

# remove insignificant variable - employees

infrastructure_model3 <-lm(log_total_inbound_tourism_expenditure~
                           occupancy_rate_per_room+
                           occupancy_rate_per_bed_place+
                           establishments+
                           hdi_code+
                           world_region, 
                         data = tourism_df)

summary(infrastructure_model3)

vif(infrastructure_model3)

#optimized, predictors with adverse VIFs have been removed, r-squared & adjusted increased slightly
```

### Model Assumptions

```{r, fig.height=7.5, fig.width = 15}
##########################
## linearity assumption ##
##########################

p1 <- ggplot(tourism_df, aes(x = occupancy_rate_per_room, y = log_total_inbound_tourism_expenditure)) +
  geom_point(color = "navy", alpha = 0.8) + 
  geom_smooth(method = "lm", se = F, color = "red") +
  theme_minimal() +
  labs(x = "Occupancy Rate per Room", y = "ln(Tourism Income)") +
  theme(axis.title = element_text(face = "bold"))

p2 <- ggplot(tourism_df, aes(x = occupancy_rate_per_bed_place, y = log_total_inbound_tourism_expenditure)) +
  geom_point(color = "navy", alpha = 0.8) + 
  geom_smooth(method = "lm", se = F, color = "red") +
  theme_minimal() +
  labs(x = "Occupancy Rate per Bed Place", y = "ln(Tourism Income)") +
  theme(axis.title = element_text(face = "bold"))

p3 <- ggplot(tourism_df, aes(x = establishments, y = log_total_inbound_tourism_expenditure)) +
  geom_point(color = "navy", alpha = 0.8) + 
  geom_smooth(method = "lm", se = F, color = "red") +
  #scale_x_continuous(limits = c(0,20000)) +
  theme_minimal() +
  labs(x = "Number of Establishments", y = "ln(Tourism Income)") +
  theme(axis.title = element_text(face = "bold"))

grid.arrange(p1,p2,p3, nrow = 2)
```

```{r, fig.width=7, fig.height = 6}
infrastructure_model_df <- tourism_df %>% 
  dplyr::select(occupancy_rate_per_bed_place,occupancy_rate_per_room,establishments,hdi_code,world_region,
                log_total_inbound_tourism_expenditure,total_inbound_tourism_expenditure,country,year) %>%
  na.omit()

infrastructure_final_model <- lm(log_total_inbound_tourism_expenditure~
                           occupancy_rate_per_room+
                           occupancy_rate_per_bed_place+
                           establishments+
                           hdi_code+
                           world_region, 
                         data = infrastructure_model_df)

# predictions, residuals on fitted model
infrastructure_model_preds <- mutate(infrastructure_model_df, 
                             predictions = fitted(infrastructure_final_model), 
                             resid = residuals(infrastructure_final_model))

# residual plot
ggplot(infrastructure_model_preds, aes(x = predictions, y = resid)) +
  geom_hline(yintercept = 0, color = "red", size = 1.1) +
  geom_point(size = 2.5, alpha = 0.5) +
  labs(x = "Predicted ln(Tourism Income)", y = "Residual") +
  #scale_x_continuous(limits = c(0,50000))
  theme_minimal() +
  theme(strip.background = element_rect(fill="gray90"),
        strip.text = element_text(size = 18, face = "bold")) +
  theme(axis.title = element_text(face = "bold"))

## qq plot
ggplot(infrastructure_model_preds, aes(sample = resid)) +
  stat_qq_line(size = 1, color = "red") +
  stat_qq(size = 3, alpha = 0.6) +
  labs(x = "Theoretical", y = "Sample") +
  theme_minimal() +
  theme(strip.background = element_rect(fill="gray90"),
        strip.text = element_text(size = 18, face = "bold")) +
  theme(axis.title = element_text(face = "bold"))
```

### Model Training

```{r, warning=FALSE}
####################
## model training ##
####################
set.seed(6021)

# use trainControl() function for applying cross validation methods
control <- trainControl(method = "repeatedcv", number = 10, repeats = 100)

# train model, with control cv function
infrastructure_trained_model <- train(log_total_inbound_tourism_expenditure~
                                occupancy_rate_per_room+
                                occupancy_rate_per_bed_place+
                                establishments+
                                hdi_code+
                                world_region, 
                              method = "lm", trControl = control, data = infrastructure_model_df)

# model summary
summary(infrastructure_trained_model)
```

### Predictions and Model Assessment

```{r}
set.seed(6021)

# model assessment
infrastructure_trained_model$results$RMSE
infrastructure_trained_model$results$Rsquared
infrastructure_trained_model$results$MAE

# make predictions
predictions <- exp(predict(infrastructure_trained_model, infrastructure_model_df))

# get predictions interval into data frame
pred_intervals <- data.frame(exp(predict(infrastructure_trained_model, 
                                         newdata = infrastructure_model_df, 
                                         interval = "prediction", level = 0.95)))
colnames(pred_intervals) <- "predicted"

# display outcomes
pred_df <- infrastructure_model_df %>% 
  dplyr::select(country, year, total_inbound_tourism_expenditure) %>% 
  mutate(pred = pred_intervals$predicted)

pred_df_view <- pred_df[sample.int(nrow(pred_df), 10),] 

pred_df_view <- pred_df_view %>% 
  rename(observed = total_inbound_tourism_expenditure)

# summarize predictions results
results <- infrastructure_model_df %>% 
  mutate(preds = predictions,
         observed = total_inbound_tourism_expenditure) %>% 
  mutate(diff = observed - preds,
         abs_diff = abs(observed - preds)) %>% 
  mutate(pct_diff = 100 * (abs_diff / abs(observed))) 

# get RMSE, MAE and MAPE on predicted values, non-log
print(paste0("RMSE: ",round(sqrt(mean(results$diff^2)), 3)))
print(paste0("MAE: ",round(mean(results$abs_diff),3)))
print(paste0("MAPE: ",round(mean(results$pct_diff),3),"%"))
```

## Logistic Regression Model - Infrasturcture and Macroeconomic Growth to Predict Tourism Growth

### Initial Model
```{r}
logit_model_df <- tourism_df %>% 
  dplyr::select(country,
                year,
                tourism_grew,
                total_arrivals_growth,
                establishments_growth,
                tourism_employees_growth,
                gdp_per_capita_growth,
                gdp_growth,
                cpi_growth,
                exchange_rate_growth,
                unemployment_rate_growth,
                hdi_growth,
                hdi_code,
                world_region
                ) %>% 
  na.omit()

logit_model <- glm(tourism_grew~.-country-year
                   , data = logit_model_df, family = "binomial")

summary(logit_model)
```

### Variable Selection
```{r}
logit_aic <- MASS::stepAIC(logit_model, direction = "both", trace = F)
summary(logit_aic)
```

```{r}
car::vif(logit_aic)
```

### Model Training
```{r}
####################
## model training ##
####################

set.seed(6021)

# use trainControl() function for applying cross validation methods
control <- trainControl(method = "cv", 
                     number = 10, 
                     summaryFunction = twoClassSummary, 
                     classProbs = T,
                     savePredictions = T
                     )

# train model, with control cv function
logit_trained_model <- train(tourism_grew~
                               total_arrivals_growth+
                               gdp_growth+
                               cpi_growth+
                               exchange_rate_growth+
                               unemployment_rate_growth,
                               #hdi_code,
                      data = logit_model_df, method = "glm", family = "binomial", 
                      trControl = control, metric = "ROC")

summary(logit_trained_model)
```

### Model Assumptions

```{r, fig.height=6.7, fig.width = 13.3}
# combine results
results <- logit_model_df %>% 
  mutate(prob = predict(logit_trained_model, logit_model_df, type = "prob")[,2]) %>% 
  mutate(odds = log(prob / (1-prob))) %>% 
  mutate(pred = ifelse(prob >= 0.50, 1, 0))

p1 <- ggplot(results, aes(x = gdp_growth, y = odds)) +
  geom_point(color = "navy", alpha = 0.8) + 
  geom_smooth(method = "lm", se = F, color = "red") +
  scale_x_continuous(limits = c(-0.05,0.1)) +
  theme_minimal() +
  labs(x = "GDP Growth", y = "Odds") +
  theme(axis.title = element_text(face = "bold"))

p2 <- ggplot(results, aes(x = cpi_growth, y = odds)) +
  geom_point(color = "navy", alpha = 0.8) + 
  geom_smooth(method = "lm", se = F, color = "red") +
  scale_x_continuous(limits = c(-0.03,0.12)) +
  scale_y_continuous(limits = c(-5, 5)) +
  theme_minimal() +
  labs(x = "CPI Growth", y = "Odds") +
  theme(axis.title = element_text(face = "bold"))

p3 <- ggplot(results, aes(x = exchange_rate_growth, y = odds)) +
  geom_point(color = "navy", alpha = 0.8) + 
  geom_smooth(method = "lm", se = F, color = "red") +
  scale_x_continuous(limits = c(-0.25,0.25)) +
  scale_y_continuous(limits = c(-5, 5)) +
  theme_minimal() +
  labs(x = "Exchange Rate Growth", y = "Odds") +
  theme(axis.title = element_text(face = "bold"))

p4 <- ggplot(results, aes(x = unemployment_rate_growth, y = odds)) +
  geom_point(color = "navy", alpha = 0.8) + 
  geom_smooth(method = "lm", se = F, color = "red") +
  scale_x_continuous(limits = c(-0.3,0.4)) +
  scale_y_continuous(limits = c(-5, 5)) +
  theme_minimal() +
  labs(x = "Unemployment Rate Growth", y = "Odds") +
  theme(axis.title = element_text(face = "bold"))

grid.arrange(p1,p2,p3,p4, nrow = 2)
```

### Predictions and Model Assessment

#### Confusion Matrix, ROC Curve
```{r, fig.width=7, fig.height = 6}

set.seed(6021)

# confusion matrix
predictions <- logit_trained_model$pred
table(predictions$pred, predictions$obs)

roc <- roc(predictions$obs, predictions$Y)

roc_dat <- data.frame(TPR = roc$sensitivities, FPR = 1 - roc$specificities)

ggplot(roc_dat, aes(x = FPR, y = TPR)) +
  geom_smooth(se = F, color = "navy") +
  labs(x = "False Positive Rate", y = "True Positive Rate") +
  theme_minimal() +
  theme(axis.title = element_text(face = "bold")) +
  annotate("text", x = 0.13, y = 0.9, size = 6, label = paste("AUC =",round(roc$auc[1],4)), fontface = "italic")
```

#### Accuracy Rates

```{r}
# accuracy rate
print(paste0("Accuracy: ",
             round(100*nrow(filter(predictions, pred == obs)) / nrow(predictions),2),
             "%"))

# true positive rate
print(paste0("True Positive Rate: ", 
             round(100*nrow(filter(predictions, pred == "Y" & obs == "Y")) /
               nrow(filter(predictions, obs == "Y")),2),
             "%"))

# true negative rate
print(paste0("True Negative Rate: ", 
             round(100*nrow(filter(predictions, pred == "N" & obs == "N")) /
               nrow(filter(predictions, obs == "N")),2),
             "%"))

# false negative rate
print(paste0("False Negative Rate: ", 
             round(100*nrow(filter(predictions, pred == "N" & obs == "Y")) /
               nrow(filter(predictions, obs == "Y")),2),
             "%"))

# false positive rate
print(paste0("False Positive Rate: ", 
             round(100*nrow(filter(predictions, pred == "Y" & obs == "N")) /
               nrow(filter(predictions, obs == "N")),2),
             "%"))

# f-1 score

precision <- 300/(300+130)
recall <- 300 /(300+128)

2*((precision*recall)/(precision+recall))
```

# Appendix

## Principle Component Regression

```{r}
####################
## model training ##
####################

# 80% and 20% training and testing split
train_split <- sample(x = 1:nrow(income_model_df), size = floor(0.8 * nrow(income_model_df)))
training_data <- income_model_df[train_split,]
testing_data <- income_model_df[-train_split,]

# train regression model with cross validation
pca_model <- pcr(log(total_inbound_tourism_expenditure)~
                        gdp_per_capita+
                        log(gdp)+
                        cpi+
                        hdi+
                        unemployment_rate+
                        log(gdp)*hdi_code+
                        log(gdp)*world_region+
                        cpi*hdi_code+
                        cpi*world_region+
                        hdi_code+
                        world_region, data = training_data, scale = T, validation  = "CV")
```

```{r}
# model summary
summary(pca_model)

# use validation plot for choosing number of components
validationplot(pca_model, val.type = "MSE")
```

```{r}
# make predictions on testing data
predictions <- exp(predict(pca_model, newdata = testing_data, ncomp = 11))

# mean absolute percentage error (MAPE)
mape <- mean( 100 * abs((testing_data$total_inbound_tourism_expenditure - predictions) /
                          testing_data$total_inbound_tourism_expenditure) )

print(paste0("MAPE: ",round(mape,2),"%"))
```

## In Progress Models

```{r}
arrivals_model <- lm(total_arrivals~gdp_per_capita+gdp+exchange_rate+cpi+hdi+hdi_code, data = tourism_df)
summary(arrivals_model)

arrivals_growth_model <- lm(total_arrivals_growth~gdp_per_capita_growth+gdp_growth+exchange_rate_growth+cpi_growth+hdi_growth+hdi_code, data = tourism_df)
summary(arrivals_growth_model)

income_growth_model <- lm(inbound_tourism_expenditure_growth~gdp_per_capita_growth+gdp_growth+exchange_rate_growth+cpi_growth+hdi_growth+tourism_employees_growth, data = tourism_df)
summary(income_growth_model)
```
